It's all about Meaning!\\{\normalsize A Theory for Data Migration during Software Development

### 2022-12-13 2022 Migration/articleMigration.tex
wip

   To complete the semantics,
   we also define a rule, {\tt EnrollRule}, that states that a student can enroll for any module that is part of a course that a student takes.
   In Ampersand, which is a syntactically sugared form of relation algebra,
   we give each rule a name and declare a role to preserve its invariance:
\begin{verbatim}
RULE EnrollRule: isEnrolledFor |- takes;isPartOf~
ROLE Administrator MAINTAINS EnrollRule
\end{verbatim}
   The semantics of Ampersand defines $\sat{\tt EnrollRule}{\dataset}$ as follows:
\begin{equation}
   \begin{array}{l}
   \forall \pair{s}{m}\in\pop{\tt isEnrolledFor}{\dataset}\ \exists c\in\text{\tt Course}:\\
s\ \text{\tt isEnrolledFor}\ m\ \rightarrow\ s\ \text{\tt takes}\ c\ \wedge\ m\ \text{\tt isPartOf}\ c
\end{array}
\label{eqn:example isEnrolledFor}
\end{equation}
   Rule {\tt EnrollRule} is satisfied because relation $\declare{\tt isEnrolledFor}{\tt Student}{\tt Module}$ is empty.

>>>>

   To complete the semantics,
   we also define a rule, {\tt EnrollRule}, that states that a student can enroll for any module that is part of a course that student takes.
   In Ampersand, which is a syntactically sugared form of relation algebra~\cite{JoostenRAMiCS2017},
   we give each rule a name and declare a role to preserve its invariance:
\begin{verbatim}
RULE EnrollRule: isEnrolledFor |- takes;isPartOf~
ROLE Administrator MAINTAINS EnrollRule
\end{verbatim}
   The semantics of this rule defines $\sat{\tt EnrollRule}{\dataset}$ as:
\begin{equation}
   \begin{array}{l}
   \forall \pair{s}{m}\in\pop{\tt isEnrolledFor}{\dataset}\ \exists c\in\text{\tt Course}:\\
s\ \text{\tt isEnrolledFor}\ m\ \rightarrow\ s\ \text{\tt takes}\ c\ \wedge\ m\ \text{\tt isPartOf}\ c
\end{array}
\label{eqn:example isEnrolledFor}
\end{equation}
   Rule {\tt EnrollRule} is satisfied because relation $\declare{\tt isEnrolledFor}{\tt Student}{\tt Module}$ is empty.
